### 2022-05-05 supplement.Rmd
Add profile likelihood plots

@@

# Save the plot
ggsave(here(figures_dir, "forest_gender.pdf"), width = 12, height = 8)
```

@@

# Save the plot
ggsave(here(figures_dir, "trace.pdf"), width = 12, height = 6)
```

@@

>>>>

# Get profile likelihoods for sigmas to check that REML has converged
prof_liks <- profile(res_freq, plot = FALSE)

@@

# Save the plot
ggsave(here(figures_dir, "figs1_gender.pdf"), width = 12, height = 8)
```

@@

# Save the plot
ggsave(here(figures_dir, "figs2_convergence.pdf"), width = 12, height = 6)
```

@@

```{r, figs3, include=TRUE, fig.height=4, fig.width=12, fig.cap="(ref:figs3-caption)"}
# Combine profile likelihood results into one data frame
prof_liks %>%
  head(-1) %>% # Remove the `comp` element
  map(~ tibble(sigma2 = .$sigma2, ll = .$ll)) %>%
  bind_rows(.id = "parameter") %>%
  # Create new labels for plotting
  mutate(parameter = factor(
    parameter,
    levels = c(1, 2),
    labels = c("italic(sigma)[article]^2", "italic(sigma)[experiment]^2")
  )) -> prof_liks_df

# Find the best-fitting parameter estimates
prof_liks_df %>%
  group_by(parameter) %>%
  filter(ll == max(ll)) -> prof_liks_max

# Create plot
prof_liks_df %>%
  ggplot(aes(x = sigma2, y = ll)) +
  facet_wrap(~parameter, scales = "free", labeller = label_parsed) +
  # Best fitting parameters
  geom_hline(
    aes(yintercept = ll),
    data = prof_liks_max, linetype = "dashed"
  ) +
  geom_vline(
    aes(xintercept = sigma2),
    data = prof_liks_max, linetype = "dashed"
  ) +
  # All tested parameters
  geom_point() +
  geom_line() +
  # Styling
  labs(x = "Parameter value", y = "Restricted log-likelihood") +
  theme_classic() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    strip.background = element_blank(),
    text = element_text(family = "Helvetica", color = "black")
  )

# Save the plot
ggsave(here(figures_dir, "figs3_convergence_freq.pdf"), width = 12, height = 4)
```

(ref:figs3-caption) **Convergence checks for the frequentist meta-analysis.** Profile likelihood plots [@raue2009; @viechtbauer2010] indicate that restricted maximum likelihood estimation (REML) was able to identify the most likely parameter estimates for the two variance components in the three-level meta-analytic model, that is, for the between-article variance and for the between-experiment (within-article) variance.
